---
title: "Comprehensive Engineering EducationIn-line learning and the Importance of Enclosing Environments in Education"
author: "Jason K Freels"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The purpose of education is give students knowledge, skills, and abilities (KSAs) such that they can produce greater results in their post-education endeavors. The KSAs required for each student depend on what they need to do.  However, with much of education seemingly moving to an online format, certain skills are required for all educators   to to build is is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

Some topics lend themself to being taught in an online format 

Equation typesetting
programming skills
student-student interactions
student-teacher interactions

Understanding the importance of enclosing environments

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
